---
title: "R Notebook"
output: html_notebook
---

New try to merge wind data from site 62 together with general data from site 72. Problem is that timestamps are not the same. 


downloading the two datasets and formatting timeseries
```{r}
dev72 <- read.csv("SN00072_26feb19-26feb20.csv", header = TRUE)
dev62 <- read.csv("WIND_62_26feb19-26feb20.csv", header = TRUE)

```

```{r}
library(anytime)
dev72$timestamp_local <- anytime(as.factor(dev72$timestamp_local))
dev62$timestamp_local <- anytime(as.factor(dev62$timestamp_local))
```



Merging directly on timestamps, not good
```{r}
time72 <- dev72$timestamp_local
time62 <- dev62$timestamp_local

# exact matching results in insane loss of time
secMerge <- merge(dev72,
                  dev62,
                  by = "timestamp_local")
length(secMerge$timestamp_local)
```
this results in a exact matching of timestamps which only yields ca 2000 datapoints...



Merging after rounding to closest minute
```{r}
# Merge works reeeeeally fast

# creating new vectors to work with
dev72_min <- dev72
dev62_min <- dev62

# rounding to closest minutes, meaning all values will end on :00
dev72_min$timestamp_local <- as.POSIXct(round(dev72_min$timestamp_local, units = "min"))
dev62_min$timestamp_local <- as.POSIXct(round(dev62_min$timestamp_local, units = "min"))

#merging together dataframes, getting joint timestamps. Now one could use y.wind_dir and y.wind_speed together with any x. values

minuteMerge <- merge(dev72_min,
                  dev62_min,
                  by = "timestamp_local")

# loss of about 70,000 timestasds
length(minuteMerge$timestamp_local)
length(dev72$timestamp_local)
length(dev62$timestamp_local)

# So i would actually only need the timestamps and winddata from minutemerge and then get that into a new datafram with all pollution data from dev72, and then find a way to "fill in the blanks" of wind data, possibly with the last known value or some kind of extrapolation?




```



A way of creating time intervalls
```{r}
# Creating a 10s intervall from a datetime x 
j <- 5
i <- (x-j)%--%(x+j)


```





Attempting a left join with dplyr library - not even started - 
```{r}
library(dplyr)
dplr <- left_join()


```





```{r}
# Too slow, might be because I dont understand 



#  Based on following solution:
#  https://stackoverflow.com/questions/42507882/merge-two-dataframes-if-timestamp-of-x-is-#  within-time-interval-of-y

# Again, creating new dataframes, this time stripping down 62 to hopefully speed things up

#variable for interval length, length = tdiff*2
tdiff <- 5

# full version of 72
sqldev72 <- dev72


# short version of 72
library(dplyr)
sqldev72_s <- slice(sqldev72, 1:100)


# pulling relevant columns from dev62 to new data frame sqldev62
# also creatign columns for interval check. Easy to manage via tdiff 
ws_62 <- dev62$wind_speed
wd_62 <- dev62$wind_dir
tsl_62 <- dev62$timestamp_local
start_time <- tsl_62-tdiff
end_time <- tsl_62+tdiff
sqldev62 <- data.frame(ws_62,wd_62,tsl_62, start_time, end_time)

# creating shorter data frames for quicker testing
library(dplyr)
sqldev72_s <- slice(sqldev72, 1:100)
sqldev62_s <- slice(sqldev62, 1:100)



library(sqldf)

dev72_w62_s <- sqldf('select *
              from sqldev72_s
              left join sqldev62_s
              on sqldev72_s.timestamp_local >= sqldev62_s.start_time
              AND sqldev72_s.timestamp_local <= sqldev62_s.end_time
          ')

# Tar 
dev72_w62 <- sqldf('select *
              from sqldev72
              left join sqldev62
              on sqldev72.timestamp_local >= sqldev62.start_time
              AND sqldev72.timestamp_local <= sqldev62.end_time
          ')

dev72_w62

```





```{r}
From Example 
https://stackoverflow.com/questions/42507882/merge-two-dataframes-if-timestamp-of-x-is-within-time-interval-of-y
```{r}
DF1 <- structure(list(Airspeed = c(582L, 478L, 524L),
                      Outbound.Track = c(119L, 78L,134L),
                      Rem.Ground.Dist = c(369L, 119L, 196L),
                      Timestamp=structure(c(1451636817.52577,
                                            1451638203.76569,
                                            1451637753.43511),
                      class = c("POSIXct", "POSIXt"), tzone = "")),
                      .Names =c("Airspeed",
                                "Outbound.Track",
                                "Rem.Ground.Dist",
                                "Timestamp"),
                      row.names =c(1L, 12L, 7L),
                      class = c("data.table", "data.frame"))

DF2 <- structure(list(Temperature = c(-18.5, -60, -35),
                      Wind_Direction = c("324", "335", "313"),
                      Wind_Speed = c("032", "041", "056"),
                      onebef =structure(c(1451629620, 1451634660, 1451637000),
                                        class = c("POSIXct", "POSIXt"), tzone = ""),
                      oneaft = structure(c(1451636820, 1451641860, 1451644200),
                      class =c("POSIXct", "POSIXt"))), .Names = c("Temperature",
                                                                  "Wind_Direction",
                                                                  "Wind_Speed","onebef",
                                                                  "oneaft"),
                      row.names = c(1358L, 1654L, 2068L),
                      class = "data.frame")

head(DF1)
head(DF2)

library(sqldf)

df<-sqldf('select d1.*,d2.*
           from DF1 d1
           left join DF2 d2
             on d1.Timestamp >= d2.onebef
               AND d1.Timestamp <= d2.oneaft
          ')
df

```



